---
title: "Canonical correlation"
author: "José Luis Blanco Pastor"
date: "17 August 2020"
output: html_document
---
```{r setup}
require("knitr")

knitr::opts_knit$set(cache = TRUE)

# Load r libraries
library(vegan)
library(bayou)
library(dplyr)
library(reshape2)
library(robust)
library(qvalue)
library(ggplot2)
library(qdap)
library(ggtree)


# We first set the working directory
opts_knit$set(root.dir = "my/working/directory")
options(scipen = 999)
```

```{r env_data, eval=FALSE, include=FALSE}
### Load env_data data 
env_data <- read.csv2("./data/env_data_NewNames.csv", header = T, row.names = 1)
```

```{r scale_env_data}
env_data_sc <- scale(env_data)

# check that we get mean of 0 and sd of 1
colMeans(env_data_sc, na.rm = T)  # faster version of apply(scaled.dat, 2, mean)
apply(env_data_sc, 2, sd, na.rm = T)
```

```{r pheno_data}
### Load phenotype data 
pheno_data <-read.csv2("./data/pheno_data_NewNames.csv", header =T, as.is=T, dec=",", sep=";", check.names = T, row.names = 1)

```

```{r escale_pheno_data}
pheno_data_sc <- scale(pheno_data)

# check that we get mean of 0 and sd of 1
colMeans(pheno_data_sc, na.rm = T)  # faster version of apply(scaled.dat, 2, mean)
apply(pheno_data_sc, 2, sd, na.rm = T)
```

```{r Impute_missing_data, eval=FALSE, include=FALSE}
#Calculate overall percentage of missing data
NAs <- sum(is.na(env_data_sc[,]))
Non_Nas <- sum(!is.na(env_data_sc[,]))
(NAs/(Non_Nas+NAs))*100
#Impute missing data with mean values across populations
for(i in 1:ncol(env_data_sc)){
  env_data_sc[is.na(env_data_sc[,i]), i] <- mean(env_data_sc[,i], na.rm = TRUE)
}
#Calculate overall percentage of missing data
NAs <- sum(is.na(env_data_sc[,]))
Non_Nas <- sum(!is.na(env_data_sc[,]))
(NAs/Non_Nas)*100
```

```{r Impute_missing_data2, eval=FALSE, include=FALSE}
#Calculate overall percentage of missing data
NAs <- sum(is.na(pheno_data_sc[,]))
Non_Nas <- sum(!is.na(pheno_data_sc[,]))
(NAs/(NAs+Non_Nas))*100
#Impute missing data with mean values across populations
for(i in 1:ncol(pheno_data_sc)){
  pheno_data_sc[is.na(pheno_data_sc[,i]), i] <- mean(pheno_data_sc[,i], na.rm = TRUE)
}
#Calculate overall percentage of missing data
NAs <- sum(is.na(pheno_data_sc[,]))
Non_Nas <- sum(!is.na(pheno_data_sc[,]))
(NAs/Non_Nas)*100
```

```{r cc}
### Canonical correlation 

cca <- CCorA(as.matrix(env_data_sc), as.matrix(pheno_data_sc), stand.Y=FALSE, stand.X=FALSE)
# biplot(cca, plot.type = "biplots")
``` 

```{r cc2}
load("my/working/directory/adegenet_reduced.RData") #We load cluster membership info, here I used adegenet to create clusters. # Available from the Dryad Digital Repository, https://doi.org/10.5061/dryad.0p2ngf1xk
levels(dapc2$grp) <- c("cluster1","cluster2","cluster3","cluster4","cluster5","cluster6","cluster7")
foo <- dapc2$grp
foo <- as.character.factor(foo)
foo <-foo[-c(456)] #Population not used in this study.
foo <- as.factor(foo)
rm(dapc2)

colorby <- foo
bg <- c("#696969", "#E69F00", "#56B4E9", "#009E73","#CC79A7", "#F0E442","#D55E00") # colors of our clusters

par(pty="s")
plot(cca$Cx[,c(1,2)], asp = 1, cex=0.5, lwd =.2)
points(cca$Cx[,c(1,2)], pch=21, cex=0.5, col="gray32", bg=bg[colorby], lwd =.2) # the Lperenne populations

biplot(x=cca, plot.type = "variables", col.Y = "indianred3", col.X = "#0868ac", cex = c(1,0.2), plot.axes = c(1,2), int=0.9)

View(sort(abs(cca$corr.Y.Cy[,1]), decreasing = T))
View(sort(abs(cca$corr.Y.Cy[,2]), decreasing = T))

View(sort(abs(cca$corr.X.Cx[,1]), decreasing = T))
View(sort(abs(cca$corr.X.Cx[,2]), decreasing = T))

write.csv2(cca$corr.X.Cx[,1:2], "./data/cca_pop_correlations_pheno.csv", row.names = T)
write.csv2(cca$corr.Y.Cy[,1:2], "./data/cca_pop_correlations_env.csv", row.names = T)
```

```{r CANCOR analyses reusult}
cca$CanCorr
# cca$Eigenvalues
sum(cca$Eigenvalues[1:2])/cca$Pillai
sum(cca$Eigenvalues[1:35])/cca$Pillai

```

```{r Load_genotype_data, eval=FALSE, include=FALSE}
### Load genotype data
snps <- read.csv("DataS1.csv", header = T) # Available from the Dryad Digital Repository, https://doi.org/10.5061/dryad.0p2ngf1xk

```

```{r, message=FALSE}
## Removing loci with freq < MAF (Minor Allele Frequency)
MAF <- 0.05
frequences <- colSums(snps)/(nrow(snps))
maf <- which(frequences > MAF & frequences < (1-MAF))
snps_MAF005 <- snps[,maf]

MAF <- 0.1
frequences <- colSums(snps)/(nrow(snps))
maf <- which(frequences > MAF & frequences < (1-MAF))
snps_MAF01 <- snps[,maf]
```

```{r MM_env_effect, eval=FALSE, include=FALSE}
env_eff_matrix <- matrix(nrow=dim(snps)[2], ncol=dim(env_data)[2])
colnames(env_eff_matrix) <- colnames(env_data)
rownames(env_eff_matrix) <- colnames(snps)
for (i in 1:dim(env_eff_matrix)[2]){
 preg <- lm(snps~env_data[,colnames(env_data)[i]])
 env_eff_matrix[,colnames(env_data)[i]] <- preg$coefficients[2,]
}
env_eff_matrix <- as.data.frame(env_eff_matrix)


env_eff_matrix_MAF005 <- matrix(nrow=dim(snps_MAF005)[2], ncol=dim(env_data)[2])
colnames(env_eff_matrix_MAF005) <- colnames(env_data)
rownames(env_eff_matrix_MAF005) <- colnames(snps_MAF005)
for (i in 1:dim(env_eff_matrix_MAF005)[2]){
 preg <- lm(snps_MAF005~env_data[,colnames(env_data)[i]])
 env_eff_matrix_MAF005[,colnames(env_data)[i]] <- preg$coefficients[2,]
}
env_eff_matrix_MAF005 <- as.data.frame(env_eff_matrix_MAF005)


env_eff_matrix_MAF01 <- matrix(nrow=dim(snps_MAF01)[2], ncol=dim(env_data)[2])
colnames(env_eff_matrix_MAF01) <- colnames(env_data)
rownames(env_eff_matrix_MAF01) <- colnames(snps_MAF01)
for (i in 1:dim(env_eff_matrix_MAF01)[2]){
 preg <- lm(snps_MAF01~env_data[,colnames(env_data)[i]])
 env_eff_matrix_MAF01[,colnames(env_data)[i]] <- preg$coefficients[2,]
}
env_eff_matrix_MAF01 <- as.data.frame(env_eff_matrix_MAF01)
```

```{r MM_pheno_effect, eval=FALSE, include=FALSE}
pheno_eff_matrix <- matrix(nrow=dim(snps)[2], ncol=dim(pheno_data)[2])
colnames(pheno_eff_matrix) <- colnames(pheno_data)
rownames(pheno_eff_matrix) <- colnames(snps)
for (i in 1:dim(pheno_eff_matrix)[2]){
 preg <- lm(snps~pheno_data[,colnames(pheno_data)[i]])
 pheno_eff_matrix[,colnames(pheno_data)[i]] <- preg$coefficients[2,]
}
pheno_eff_matrix <- as.data.frame(pheno_eff_matrix)


pheno_eff_matrix_MAF005 <- matrix(nrow=dim(snps_MAF005)[2], ncol=dim(pheno_data)[2])
colnames(pheno_eff_matrix_MAF005) <- colnames(pheno_data)
rownames(pheno_eff_matrix_MAF005) <- colnames(snps_MAF005)
for (i in 1:dim(pheno_eff_matrix_MAF005)[2]){
 preg <- lm(snps_MAF005~pheno_data[,colnames(pheno_data)[i]])
 pheno_eff_matrix_MAF005[,colnames(pheno_data)[i]] <- preg$coefficients[2,]
}
pheno_eff_matrix_MAF005 <- as.data.frame(pheno_eff_matrix_MAF005)


pheno_eff_matrix_MAF01 <- matrix(nrow=dim(snps_MAF01)[2], ncol=dim(pheno_data)[2])
colnames(pheno_eff_matrix_MAF01) <- colnames(pheno_data)
rownames(pheno_eff_matrix_MAF01) <- colnames(snps_MAF01)
for (i in 1:dim(pheno_eff_matrix_MAF01)[2]){
 preg <- lm(snps_MAF01~pheno_data[,colnames(pheno_data)[i]])
 pheno_eff_matrix_MAF01[,colnames(pheno_data)[i]] <- preg$coefficients[2,]
}
pheno_eff_matrix_MAF01 <- as.data.frame(pheno_eff_matrix_MAF01)

```

```{r scale_env_eff_matrix}
env_eff_matrix_sc <- scale(env_eff_matrix)
env_eff_matrix_sc_MAF005 <- scale(env_eff_matrix_MAF005)
env_eff_matrix_sc_MAF01 <- scale(env_eff_matrix_MAF01)

# check that we get mean of 0 and sd of 1
colMeans(env_eff_matrix_sc_MAF01)  # faster version of apply(scaled.dat, 2, mean)
apply(env_eff_matrix_sc_MAF01, 2, sd, na.rm = T)
```

```{r scale_pheno_eff_matrix}
pheno_eff_matrix_sc <- scale(pheno_eff_matrix)
pheno_eff_matrix_sc_MAF005 <- scale(pheno_eff_matrix_MAF005)
pheno_eff_matrix_sc_MAF01 <- scale(pheno_eff_matrix_MAF01)

# check that we get mean of 0 and sd of 1
colMeans(pheno_eff_matrix_sc_MAF01)  # faster version of apply(scaled.dat, 2, mean)
apply(pheno_eff_matrix_sc_MAF01, 2, sd, na.rm = T)
```

```{r cc_snps}
### Canonical correlation 

cca_snps <- CCorA(env_eff_matrix_sc, pheno_eff_matrix_sc, stand.Y=FALSE, stand.X=FALSE, permutations = 0)
cca_snps_MAF005 <- CCorA(env_eff_matrix_sc_MAF005, pheno_eff_matrix_sc_MAF005, stand.Y=FALSE, stand.X=FALSE, permutations = 0)
cca_snps_MAF01 <- CCorA(env_eff_matrix_sc_MAF01, pheno_eff_matrix_sc_MAF01, stand.Y=FALSE, stand.X=FALSE, permutations = 0)

# biplot(cca_snps_MAF01, plot.type = "biplots", xlabs = NULL)
``` 

## Post treatment of CANCOR results

```{r, message=FALSE}
# The function returning p-values and q-values for all the loci with ordinary lambda

CANCORtest<-function(cca_snps,K)
{
  loadings<-cca_snps$Cx[,1:as.numeric(K)]
  resscale <- apply(loadings, 2, scale)
  resmaha <- covRob(resscale, distance = TRUE, na.action= na.omit, estim="pairwiseGK")$dist
  lambda <- median(resmaha)/qchisq(0.5,df=K)
  reschi2test <- pchisq(resmaha/lambda,K,lower.tail=FALSE)
  qval <- qvalue(reschi2test)
  q.values_rdadapt<-qval$qvalues
  return(data.frame(loci=rownames(cca_snps$Cx), p.values=reschi2test, q.values=q.values_rdadapt))
}

```

```{r, message=FALSE}
# Checking alternative MAF and K values 
x1<-CANCORtest(cca_snps_MAF005, 8)
x2<-CANCORtest(cca_snps_MAF005, 4)
x3<-CANCORtest(cca_snps_MAF005, 2)

x4<-CANCORtest(cca_snps_MAF01, 8)
x5<-CANCORtest(cca_snps_MAF01, 4)
x6<-CANCORtest(cca_snps_MAF01, 2)

x7<-CANCORtest(cca_snps, 8)
x8<-CANCORtest(cca_snps, 4)
x9<-CANCORtest(cca_snps, 2)

#Histogram of p-values
par(mfrow = c(3, 3))
hist(x1$p.values, xlab="p-values", main="K8 min MAF = 0.05", breaks = 50, col = "orange")
hist(x2$p.values, xlab="p-values", main="K4 min MAF = 0.05", breaks = 50, col = "orange")
hist(x3$p.values, xlab="p-values", main="K2 min MAF = 0.05", breaks = 50, col = "orange")
hist(x4$p.values, xlab="p-values", main="K8 min MAF = 0.1", breaks = 50, col = "orange")
hist(x5$p.values, xlab="p-values", main="K4 min MAF = 0.1", breaks = 50, col = "orange")
hist(x6$p.values, xlab="p-values", main="K2 min MAF = 0.1", breaks = 50, col = "orange")
hist(x7$p.values, xlab="p-values", main="K8 min MAF = 0.0", breaks = 50, col = "orange")
hist(x8$p.values, xlab="p-values", main="K4 min MAF = 0.0", breaks = 50, col = "orange")
hist(x9$p.values, xlab="p-values", main="K2 min MAF = 0.0", breaks = 50, col = "orange")
par(mfrow = c(1, 1))
```

## Visualisation of the results

```{r, message=FALSE}
# Manhattan plot K2 min MAF=0.1 (outliers : q.value < 0.1 are colored in orange)
```
```{r, echo=TRUE, fig.align="center", fig.width=8, fig.height=8}
ggplot() +
  geom_point(aes(x=c(1:length(x6[,2])), y=-log10(x6[,2])), col = "gray83") +
  geom_point(aes(x=c(1:length(x6[,2]))[which(x6[,3] < 0.1)], y=-log10(x6[which(x6[,3] < 0.1),2])), col = "red") +
  xlab("SNPs") + ylab("-log10(p.values)") +
  theme_bw()
```
##
```{r, message=FALSE}
# Outliers loci (q.values < 0.1)

length(which(x6[,3] < 0.1))
length(which(x6[,3] > 0.1))

# Candidates, p-values and q-values
View(x6[x6[,3] < 0.1,])

test_pass <- as.character(x6[x6[,3] < 0.1,]$loci)
```


```{r}
#CANCOR plot - CANCOR outliers highlighted

snps2 <- as.data.frame(t(snps_MAF01))
snps2$CANCOR_test <- ifelse(rownames(snps2) %in% test_pass, "CANCOR_significant","CANCOR_not_significant")
length(which(snps2$CANCOR_test == "GWAS_significant"))

snps2$CANCOR_test <- as.factor(snps2$CANCOR_test)
levels(snps2$CANCOR_test) 

colorby <- snps2$CANCOR_test
bg <- c(makeTransparent("grey", alpha =0), "darkorchid1")
col <- c(makeTransparent("grey", alpha =0), "black") 


par(pty="s")
plot(cca_snps_MAF01$Cx[,c(1,2)], asp = 1, pch=21, col=makeTransparent("black"), cex=.5, bg=makeTransparent("grey"), lwd =.0001)
points(cca_snps_MAF01$Cx[,c(1,2)], pch=21, col=col[colorby], cex=0.5, bg=bg[colorby],lwd =.0001) # the GWAS-significant adaptive loci
biplot(x=cca_snps_MAF01, plot.type = "variables", col.Y = "indianred3", col.X = "#0868ac", cex = c(1,0.2), plot.axes = c(1,2), int = .9)
```

```{r}
View(sort(abs(cca_snps_MAF01$corr.Y.Cy[,1]), decreasing = T))
View(sort(abs(cca_snps_MAF01$corr.Y.Cy[,2]), decreasing = T))
View(sort(abs(cca_snps_MAF01$corr.Y.Cy[,3]), decreasing = T))
View(sort(abs(cca_snps_MAF01$corr.Y.Cy[,4]), decreasing = T))

View(sort(abs(cca_snps_MAF01$corr.X.Cx[,1]), decreasing = T))
View(sort(abs(cca_snps_MAF01$corr.X.Cx[,2]), decreasing = T))
View(sort(abs(cca_snps_MAF01$corr.X.Cx[,3]), decreasing = T))


write.csv2(cca_snps_MAF01$corr.X.Cx[,c(1,2)], "./data/cca_all_snp_correlations_pheno_1_2.csv", row.names = T)
write.csv2(cca_snps_MAF01$corr.Y.Cy[,c(1,2)], "./data/cca_all_snp_correlations_env_1_2.csv", row.names = T)

# Table of object scores in env variable plot (Y)
write.csv2(cca_snps_MAF01$Cy[,c(1,2)], "./data/cca_snp_all_scores_Y_plot_1_2.csv", row.names = T)
```

```{r CANCOR analyses reusult}
cca_snps_MAF01$CanCorr
# cca_snps_MAF01$Eigenvalues
sum(cca_snps_MAF01$Eigenvalues[1:2])/cca_snps$Pillai
sum(cca_snps_MAF01$Eigenvalues[1:38])/cca_snps$Pillai
```

## CANDIDATES data frame
```{r load_rda_axis, eval=FALSE, include=FALSE}
load.cancor <- cca_snps_MAF01$Cx[,1:2]  # Species scores for the first two constrained axes of the phenotype data table
load.cancor_pass <- load.cancor[rownames(load.cancor) %in% test_pass, ]
```

Let's add in the correlations of each candidate SNP with the 112 environmental predictors:
```{r, outliers_df2}
foo <- matrix(nrow=nrow(load.cancor_pass), ncol=112)  # 112 columns for 112 predictors
colnames(foo) <- colnames(env_data) 

for (i in 1:length(rownames(load.cancor_pass))) {
  nam <- rownames(load.cancor_pass)[i]
  snp.gen <- snps[,nam]
  foo[i,] <- apply(env_data,2,function(x) {
  cor.result<- cor.test(x,snp.gen)
  cor.result$estimate
    # estimate <- cor.result$estimate)
})
}
cand <- cbind.data.frame(load.cancor_pass,foo)  
head(cand)
```
Now we have a data frame of 631 candidate SNPs and their correlation with our 112 environmental predictors.


Let's add in the correlation p-values of each candidate SNP with the 112 environmental predictors:
```{r, outliers_pvalue_df2}
foo_pvalue <- matrix(nrow=nrow(load.cancor_pass), ncol=112)  # 112 columns for 112 predictors
colnames(foo_pvalue) <- colnames(env_data) 

for (i in 1:length(rownames(load.cancor_pass))) {
  nam <- rownames(load.cancor_pass)[i]
  snp.gen <- snps[,nam]
  foo_pvalue[i,] <- apply(env_data,2,function(x) {
  cor.result<- cor.test(x,snp.gen)
  cor.result$p.value
    # estimate <- cor.result$estimate)
})
}
cand_pvalues <- cbind.data.frame(load.cancor_pass,foo_pvalue)  
head(cand_pvalues)
```
Now we have a data frame of 631 candidate SNPs and their correlation test pvalues with our 112 environmental predictors.

## Investigate the candidates 

Next, we'll see which of the predictors each candidate SNP is correlated with:
```{r, correlations}
for (i in 1:length(rownames(cand))) {
  bar <- cand[i,]
  ids_pos <- which(bar[3:114] > 0.5,arr.ind=TRUE) # gives the variable
  ids_neg <- which(bar[3:114] < -0.5,arr.ind=TRUE) # gives the variable

  cand[i,115] <- paste(colnames(bar[3:114])[ids_pos[,"col"]], collapse = ",")
  cand[i,116] <- paste(colnames(bar[3:114])[ids_neg[,"col"]], collapse = ",")

}

colnames(cand)[115] <- "Highly positively correlated with (Environmental variable)"
colnames(cand)[116] <- "Highly negatively correlated with (Environmental variable)"

head(cand, n=100) 
```
Most of the candidates are correlated with several environmental variables


Next, we'll see which of the predictors each candidate SNP is MOST STRONGLY correlated with:
```{r, correlations2}
for (i in 1:length(rownames(cand))) {
  bar <- cand[i,]
  cand[i,117] <- names(which.max(abs(bar[3:114]))) # gives the variable
  cand[i,118] <- max(abs(bar[3:114]))              # gives the correlation
}

colnames(cand)[117] <- "Environmental variable (strongest correlation)"
colnames(cand)[118] <- "Correlation value (Environmental variable)"

head(cand, n=100)
```

Let's add in the correlations of each candidate SNP with the 145 phenotypic traits:
```{r, outliers_df2b}
foo <- matrix(nrow=nrow(load.cancor_pass), ncol=145)  # 145 columns for 145 predictors
colnames(foo) <- colnames(pheno_data) 

for (i in 1:length(rownames(load.cancor_pass))) {
  nam <- rownames(load.cancor_pass)[i]
  snp.gen <- snps[,nam]
  foo[i,] <- apply(pheno_data,2,function(x) {
  cor.result<- cor.test(x,snp.gen)
  cor.result$estimate
    # estimate <- cor.result$estimate
})
}
candb <- cbind.data.frame(load.cancor_pass,foo)  
head(candb)
```
Now we have a data frame of 631 candidate SNPs and their correlation with our 145 environmental predictors.

Let's add in the correlation p-values of each candidate SNP with the 145 environmental predictors:
```{r, outliers_pvalue_df2b}
foo_pvalue <- matrix(nrow=nrow(load.cancor_pass), ncol=145)  # 145 columns for 145 predictors
colnames(foo_pvalue) <- colnames(pheno_data) 

for (i in 1:length(rownames(load.cancor_pass))) {
  nam <- rownames(load.cancor_pass)[i]
  snp.gen <- snps[,nam]
  foo_pvalue[i,] <- apply(pheno_data,2,function(x) {
  cor.result<- cor.test(x,snp.gen)
  cor.result$p.value
    # estimate <- cor.result$estimate)
})
}
cand_pvaluesb <- cbind.data.frame(load.cancor_pass,foo_pvalue)  
head(cand_pvaluesb)
```
Now we have a data frame of 631 candidate SNPs and their correlation test pvalues with our 145 environmental predictors.

## Investigate the candidates 

Next, we'll see which of the predictors each candidate SNP is correlated with r>0.5:
```{r, correlationsb}
for (i in 1:length(rownames(candb))) {
  bar <- candb[i,]
  ids_pos <- which(bar[3:147] > 0.5,arr.ind=TRUE) # gives the variable
  ids_neg <- which(bar[3:147] < -0.5,arr.ind=TRUE) # gives the variable

  candb[i,148] <- paste(colnames(bar[3:147])[ids_pos[,"col"]], collapse = ",")
  candb[i,149] <- paste(colnames(bar[3:147])[ids_neg[,"col"]], collapse = ",")

}

colnames(candb)[148] <- "Highly positively correlated with (Phenotypic variable)"
colnames(candb)[149] <- "Highly negatively correlated with (Phenotypic variable)"

head(candb, n=100) 
```

Most of the candidates are correlated with several phenotypic variables

Next, we'll see which of the predictors each candidate SNP is MOST STRONGLY correlated with:
```{r, correlations2b}
for (i in 1:length(rownames(candb))) {
  bar <- candb[i,]
  candb[i,150] <- names(which.max(abs(bar[3:147]))) # gives the variable
  candb[i,151] <- max(abs(bar[3:147]))              # gives the correlation
}

colnames(candb)[150] <- "Phenotypic variable (strongest correlation)"
colnames(candb)[151] <- "Correlation value (Phenotypic variable)"

head(candb, n=100)
```

```{r, correlations3}
cand2 <- cbind(cand[,c(1:2,115:116)], candb[,c(148:149)], stringsAsFactors=F)

head(cand2, n=100)

```


## Plot the SNPs
Let's look at CANCOR plots again, but this time focus in on the SNPs in the ordination space. We'll color code the SNPs based on the predictor variable that they are most strongly correlated with. 
```{r, snp.plot1, fig.width=16, fig.height=16, fig.show='hold'}
clim_vector_lenght_on_plane_1_2 <- sqrt((abs(cca_snps$corr.Y.Cy[,1])^2) + (abs(cca_snps$corr.Y.Cy[,2])^2))
clim_high_vector_lenght_on_plane_1_2 <- names(clim_vector_lenght_on_plane_1_2[clim_vector_lenght_on_plane_1_2 > 0.95])

pheno_vector_lenght_on_plane_1_2 <- sqrt((abs(cca_snps$corr.X.Cx[,1])^2) + (abs(cca_snps$corr.X.Cx[,2])^2))
pheno_high_vector_lenght_on_plane_1_2 <- names(pheno_vector_lenght_on_plane_1_2[pheno_vector_lenght_on_plane_1_2 > 0.9])

#Add extra variables not reaching 0.9 length but representative of al portions of the plane

clim <- sort(c(clim_high_vector_lenght_on_plane_1_2, "daily_ws", "dgrb"))
pheno <- sort(c(pheno_high_vector_lenght_on_plane_1_2, "HEA_avg", "HFY_avg", "WSC_avg", "PRT_avg", "NSL_lu17"))

png("data/CANCOR_outliers_clim.png",width=16,height=16, units = "in", res = 600)
par(pty="s", mfrow=c(6,4))

for (i in 1:length(clim)){
cand2[[clim[i]]] <- ifelse(grepl(clim[i], cand2$`Highly positively correlated with (Environmental variable)`), clim[i],NA)
cand2[[clim[i]]] <- as.factor(cand2[[clim[i]]])

colorby <- cand2[[clim[i]]]
bg <- c("darkorchid1") # colors of our clusters
col <- c("black") # colors of our clusters

cand2[[clim[i]]] <- ifelse(grepl(clim[i], cand2$`Highly negatively correlated with (Environmental variable)`), clim[i],NA)
cand2[[clim[i]]] <- as.factor(cand2[[clim[i]]])

colorby2 <- cand2[[clim[i]]]
bg2 <- c("springgreen") # colors of our clusters

plot(cca_snps_MAF01$Cx[,c(1,2)], asp = 1, pch=21, col=makeTransparent("black"), cex=.5, bg=makeTransparent("grey"), lwd =.0001, main=clim[i])
points(cca_snps_MAF01$Cx[,c(1,2)][rownames(cca_snps_MAF01$Cx[,c(1,2)]) %in% rownames(cand2), ], pch=21, col=coalesce(col[colorby],col[colorby2]), cex=1, bg=coalesce(bg[colorby],bg2[colorby2]),lwd =.0001) # the GWAS-significant adaptive loci

}

dev.off()

png("data/CANCOR_outliers_pheno.png",width=16,height=16, units = "in", res = 600)
par(pty="s", mfrow=c(8,4))

for (i in 1:length(pheno)){
cand2[[pheno[i]]] <- ifelse(grepl(pheno[i], cand2$`Highly positively correlated with (Phenotypic variable)`), pheno[i],NA)
cand2[[pheno[i]]] <- as.factor(cand2[[pheno[i]]])

colorby <- cand2[[pheno[i]]]
bg <- c("darkorchid1") # colors of our clusters
col <- c("black") # colors of our clusters

cand2[[pheno[i]]] <- ifelse(grepl(pheno[i], cand2$`Highly negatively correlated with (Phenotypic variable)`), pheno[i],NA)
cand2[[pheno[i]]] <- as.factor(cand2[[pheno[i]]])

colorby2 <- cand2[[pheno[i]]]
bg2 <- c("springgreen") # colors of our clusters

plot(cca_snps_MAF01$Cx[,c(1,2)], asp = 1, pch=21, col=makeTransparent("black"), cex=.5, bg=makeTransparent("grey"), lwd =.0001, main=pheno[i])
points(cca_snps_MAF01$Cx[,c(1,2)][rownames(cca_snps_MAF01$Cx[,c(1,2)]) %in% rownames(cand2), ], pch=21, col=coalesce(col[colorby],col[colorby2]), cex=1, bg=coalesce(bg[colorby],bg2[colorby2]),lwd =.0001) # the GWAS-significant adaptive loci

}

dev.off()

#Remove variables with trait values not reaching 0.5 of correlation value with outlier allele frequencies

clim2 <- clim[!clim %in% c("dgrb","daily_ws", "pr_au")]

pheno2 <- pheno[!pheno %in% c("AHD_avg","CH300h_po17", "DES_po15", "DHE_01_lu16", "DVG_04_lu17", "HFY_avg", "NSL_lu17", "PRT_avg", "resCH300h_po17", "resCH400h_po17", "SCD_su15_lu", "VAS_po15", "WSC_avg")]

png("D:/Work data/Analyses/2016/2016_08_25_LoliumLandscapeGenetics/R/data/CANCOR_outliers_clim2b.png",width=6.95,height=16, units = "in", res = 600)
par(pty="s", mfrow=c(7,3))

for (i in 1:length(clim2)){
cand2[[clim2[i]]] <- ifelse(grepl(clim2[i], cand2$`Highly positively correlated with (Environmental variable)`), clim2[i],NA)
cand2[[clim2[i]]] <- as.factor(cand2[[clim2[i]]])

colorby <- cand2[[clim2[i]]]
bg <- c("darkorchid1") # colors of our clusters
col <- c("black") # colors of our clusters

cand2[[clim2[i]]] <- ifelse(grepl(clim2[i], cand2$`Highly negatively correlated with (Environmental variable)`), clim2[i],NA)
cand2[[clim2[i]]] <- as.factor(cand2[[clim2[i]]])

colorby2 <- cand2[[clim2[i]]]
bg2 <- c("springgreen") # colors of our clusters

plot(cca_snps_MAF01$Cy[,c(1,2)], asp = 1, pch=21, col=makeTransparent("black"), cex=.5, bg=makeTransparent("grey"), lwd =.0001, main=clim2[i])
points(cca_snps_MAF01$Cy[,c(1,2)][rownames(cca_snps_MAF01$Cy[,c(1,2)]) %in% rownames(cand2), ], pch=21, col=coalesce(col[colorby],col[colorby2]), cex=1, bg=coalesce(bg[colorby],bg2[colorby2]),lwd =.0001) # the GWAS-significant adaptive loci

}

dev.off()

png("data/CANCOR_outliers_pheno2b.png",width=6.95,height=16, units = "in", res = 600)
par(pty="s", mfrow=c(7,3))

for (i in 1:length(pheno2)){
cand2[[pheno2[i]]] <- ifelse(grepl(pheno2[i], cand2$`Highly positively correlated with (Phenotypic variable)`), pheno2[i],NA)
cand2[[pheno2[i]]] <- as.factor(cand2[[pheno2[i]]])

colorby <- cand2[[pheno2[i]]]
bg <- c("darkorchid1") # colors of our clusters
col <- c("black") # colors of our clusters

cand2[[pheno2[i]]] <- ifelse(grepl(pheno2[i], cand2$`Highly negatively correlated with (Phenotypic variable)`), pheno2[i],NA)
cand2[[pheno2[i]]] <- as.factor(cand2[[pheno2[i]]])

colorby2 <- cand2[[pheno2[i]]]
bg2 <- c("springgreen") # colors of our clusters

plot(cca_snps_MAF01$Cx[,c(1,2)], asp = 1, pch=21, col=makeTransparent("black"), cex=.5, bg=makeTransparent("grey"), lwd =.0001, main=pheno2[i])
points(cca_snps_MAF01$Cx[,c(1,2)][rownames(cca_snps_MAF01$Cx[,c(1,2)]) %in% rownames(cand2), ], pch=21, col=coalesce(col[colorby],col[colorby2]), cex=1, bg=coalesce(bg[colorby],bg2[colorby2]),lwd =.0001) # the GWAS-significant adaptive loci

}

dev.off()
```
